---
title: "Wattler R Package"
author: "Aaron Wattler"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation

Load in common libraries used by this package
```{r eval=FALSE}
library(tidyverse)
library(ggplot2)

```
Now we install my R Package
```{r eval = FALSE}
devtools::install_github("awatt008/R_Package_Wattler")
library(projects)
```

Let us download some data for our package:
```{r eval=FALSE}
download.file(url = "https://raw.githubusercontent.com/awatt008/R_Package_Wattler/master/Data/surveys.csv", destfile = "data/surveys.csv")
```
Now, we load the data
```{r eval = FALSE}
surveys <- read_csv("data/surveys.csv")
```
##Working Example

+ an example of each function and how it works
+ say something about why this is a good thing to do
+ say something about expected output
```{r eval = FALSE}
 boxplot_weight_species <- function(., species_id,weight){
      if(!is.data.frame(surveys)){
        return("This is not a dataframe")
      }
     plt <- ggplot(., mapping = aes(x = weight, y = species_id)) +
            geom_boxplot()
            return(plt)
 }
```

```{r eval = FALSE}
surveys%>%
   filter(!is.na(species_id))%>%
   filter(!is.na(weight))%>%
   select(species_id, weight) %>% 
   boxplot_weight_species(species_id = species_id, weight = weight) 

```

```{r eval = FALSE}
no_na_weight <- function(., weight){
  if(any(!is.na(surveys$weight)))
  scrub_weight_na <- surveys%>%
  filter(!is.na(weight))
return(scrub_weight_na)
}
```


```{r}
weight_loss_program <- surveys%>%
no_na_weight(weight = weight)
```

```{r weight_loss_program, echo = FALSE}
weight_loss_program
```

```{r}
hindfoot_weight_regression <- function(., weight, hindfoot_length){
  if(!is.data.frame(surveys)){
    return("This is not a dataframe")
  }
  plt_regression <- ggplot(., aes(x = weight, y = hindfoot_length)) +
    geom_point(size = .25) + 
    geom_smooth(method = "lm",     
                color = "blue",    
                size = .5,        
                fill = "black")        
  return(plt_regression)
}
```

```{r}
plot_of_regression<- surveys%>%
filter(!is.na(weight))%>%
filter(!is.na(hindfoot_length))%>%
select(weight,hindfoot_length)%>%                 
group_by(weight,hindfoot_length)%>%
hindfoot_weight_regression(weight = weight, hindfoot_length = hindfoot_length)
```

```{r plot_of_regression, echo=FALSE}

plot(plot_of_regression)
```
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
